Paper Results Section

### 2019-04-03 notebooks/jan.Rmd
minor

Load the data.
```{r, echo=FALSE}
los <- list.files("../data/full_sigs", full.names=TRUE)
names <- list.files("../data/full_sigs")
names(los) <- substr(names, 1, nchar(names)-4)
los <- lapply(los, readRDS)
los <- remove_empties(los)
# annoying strange error that I should fix pops up

# There's at least one transformation that we're always gonna want to apply, namly the vector/scalar
# collapse where both are present in a signature.
los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
# Figure out which ones are matrices. Remove if the analysis picks this up (and we rerun).
los <- lapply(los, function(lofun) lapply(lofun, distinguish_matrices_df))
```

Get the counts.
```{r}
# argument counts
c_basic_df <- build_arg_count_df_from_lopkgs(los)

xtable(c_basic_df) %>% print(include.rownames=F)
```

```{r}
# function counts
c_f_basic_df <- build_fun_count_df_from_lopkgs(los)

xtable(c_f_basic_df) %>% print(include.rownames=F)
```

Top signatures, with printing.
This is how you get the top sigs.
```{r}
poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
poly_type_args <- poly_type_args[order(-poly_type_args$count),] # sort by count
poly_type_args$perc <- round(poly_type_args$count/sum(poly_type_args$count) * 100, 2)
```

Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

Now, having noted that:
(1) ints and doubles are basically interchangable, and
(2) null and NA should be a part of every type,
while also noting that together these make up a huge portion of the polymorphism, we transform.
```{r}
los <- lapply(los, function(s) lapply(s, fold_NULL_and_NA_into_other_types_df))
null_na_fold_arg_counts <- build_arg_count_df_from_lopkgs(los)
null_na_fold_fun_counts <- build_fun_count_df_from_lopkgs(los)

los <- lapply(los, function(lof) {lapply(lof, function(df) {change_type_systems_df(df, type_map_sv_to_real)})})
null_na_fold_real_arg_counts <- build_arg_count_df_from_lopkgs(los)
null_na_fold_real_fun_counts <- build_fun_count_df_from_lopkgs(los)
```

Generate...
```{r}
xtable(null_na_fold_real_arg_counts) %>% print(include.rownames=F)
xtable(null_na_fold_real_fun_counts) %>% print(include.rownames=F)
```

Top sig time.
```{r}
poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
poly_type_args <- poly_type_args[order(-poly_type_args$count),] # sort by count
poly_type_args$perc <- round(poly_type_args$count/sum(poly_type_args$count) * 100, 2)
```

Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

Get the biggest signatures.
```{r}
lo_sizes <- get_X_biggest_functions(los, metric = size_of_signature_type)

top_10_big <- head(lo_sizes, 10)

# make df
top_10_big_df <- data.frame(
  pkg = sapply(names(top_10_big), function(n) strsplit(n, split="::")[[1]][1]),
  fun = sapply(names(top_10_big), function(n) strsplit(n, split="::")[[1]][2]),
  size = top_10_big
)

rownames(top_10_big_df) <- NULL

top_10_big_df %>% xtable

>>>>

Load the data.
```{r, echo=FALSE}
df <- list.files("../data/full_sigs", full.names=TRUE)
